Supervised Dimensionality Reduction with Random Projection-Based Ensemble Learning

### 2021-02-16 main.tex
restructuring

%\usepackage{comment}
%\newcommand{\indep}{\rotatebox[origin=c]{90}{$\models4[]}
\usepackage[colorlinks,linkcolor=red,citecolor=blue,urlcolor=blue,breaklinks = true]{hyperref}

@@

\title{Algorithms for Supervised Dimensionality Reduction with Random Projection-Based Ensemble Learning}
\author{Jacob R. Bradley, Timothy I. Cannings}
\date{}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=4in]{ExampleFigures.png}
\caption{Simple distributions that will provide a range of challenges to clustering and/or variable selection methods when embedded in higher dimensional space.\label{fig:examplefigures}}
\end{figure}

@@

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[height=2.3in]{simpleboundary.png}
        \caption{The distribution of the two classes in the first two components. All other components are identically distributed between the two classes.\label{fig:simpleboundary}}
    \end{subfigure}%

    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[height=2.3in]{simpleeigs.png}
        \caption{The sequence of average projection eigenvalues show a clear distinction for the very first basis vector.}
    \end{subfigure}
    ~ 
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[height=2.3in]{simplecomponents.png}
        \caption{Investigating the basis vector corresponding to the distinct eigenvalue shows a strong selection for the first component.}
    \end{subfigure}
\caption{}
\end{figure*}

\subsection{Case 2: Complex Separation}
\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[height=2.2in]{complexboundary.png}
        \caption{}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[height=2.2in]{complexeigs.png}
        \caption{}
    \end{subfigure}

    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[height=2.2in]{complexfirst.png}
        \caption{}
    \end{subfigure}
    ~
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[height=2.2in]{complexsecond.png}
        \caption{}
    \end{subfigure}
\caption{}
\end{figure*}
\section{Real-World Examples}
\subsection{Epilepsy Dataset}

>>>>

%\usepackage{comment}
%\newcommand{\indep}{\rotatebox[origin=c]{90}{$\models4[]}
\usepackage[colorlinks,linkcolor=black,citecolor=black,urlcolor=blue,breaklinks = true]{hyperref}

@@

\title{Supervised Dimensionality Reduction with Random Projection-Based Ensemble Learning}
\author{Jacob R. Bradley, Timothy I. Cannings}
\date{}

\setcitestyle{authoryear, open={(},close={)}}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=4in]{figures/ExampleFigures.png}
\caption{Simple distributions that will provide a range of challenges to clustering and/or variable selection methods when embedded in higher dimensional space.\label{fig:examplefigures}}
\end{figure}

@@

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[height=2.3in]{figures/simpleboundary.png}
        \caption{The distribution of the two classes in the first two components. All other components are identically distributed between the two classes.\label{fig:simpleboundary}}
    \end{subfigure}%

    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[height=2.3in]{figures/simpleeigs.png}
        \caption{The sequence of average projection eigenvalues show a clear distinction for the very first basis vector.}
    \end{subfigure}
    ~ 
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[height=2.3in]{figures/simplecomponents.png}
        \caption{Investigating the basis vector corresponding to the distinct eigenvalue shows a strong selection for the first component.}
    \end{subfigure}
\caption{}
\end{figure*}

\subsection{Case 2: Complex Separation}
\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[height=2.2in]{figures/complexboundary.png}
        \caption{}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[height=2.2in]{figures/complexeigs.png}
        \caption{}
    \end{subfigure}

    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[height=2.2in]{figures/complexfirst.png}
        \caption{}
    \end{subfigure}
    ~
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[height=2.2in]{figures/complexsecond.png}
        \caption{}
    \end{subfigure}
\caption{}
\end{figure*}
\section{Real-World Examples}
\subsection{Epilepsy Dataset}
